\sffamily An EEG-based visual Brain-Computer Interface for gaze-free communication

### 2024-09-16 chapters/bci.tex
Haemodynamic signal

Let's break this definition down and focus on the separatate representing what is happening in the brain
is the neuronal \textit{action potential}.
The brain consists 86 billion neurons, which are highly interconnected cells that are
the smallest units of information processing.
The action potential is an electrical pulse occurring when a neuron receives
input from another neuron and is activated.\todo{kort door de bocht}
A neuron's action potential, or the combined action potentials of groups of
synchronized neurons, thus generate an electrical field in and near the brain,
which can be measured using electrodes.
Fluctuations in the brain's electrical potential are a much faster and more
informative signal for our purposes.
\todo{lower part to section}
While a myriad of other techniques can be used to measure functional brain
activity, such as functional ultrasound imaging (fUS) or magnetoencephalograpy
(MEG), we'll limit ourselves in this work to measuring the electrical field.
Section~\ref{sec:bci-recording} gives an overview of current recording
technologies.\todo{make shorter, move part to section}

>>>>

Let's break this definition down and focus on its separate parts.
First of all, we need to identify a signal that is a direct representation of
what's going on in the brain.
One might for instance measure the fluctuations in blood flow to specific brain
regions that are more or less active at a given time, i.e. the
\textit{haemodynamic signal} with a scanner.
However, this signal reacts to slowly to reflect the real-time activity that is
of interest for our purposes, and it carries little information other than the
brain regions where it is originating.
A better candidate is the neuronal \textit{action potential}.
The brain consists 86 billion neurons, which are highly interconnected cells that are
the smallest units of information processing.
The action potential is an electrical pulse occurring when a neuron receives
input from another neuron and is activated.\todo{kort door de bocht}
A neuron's action potential, or the combined action potentials of groups of
synchronized neurons, thus generate an electrical field in and near the brain,
which can be measured using electrodes.
Fluctuations in the brain's electrical potential are a much faster and more
informative signal for our purposes.
\todo{lower part to section}
While a myriad of other techniques can be used to measure functional brain
activity, such as functional ultrasound imaging (fUS) or magnetoencephalograpy
(MEG), we'll limit ourselves in this work to measuring the electrical field.
Section~\ref{sec:bci-recording} gives an overview of current recording
technologies.\todo{make shorter, move part to section}
